Agile Monitoring of Evolving Web Services: For the Little Man

### 2018-04-09 discussion.tex
progressing...

  \subsection*{Limitation of Visualizations }

    The visualizations for the user experiene perspectives as presented in Section \ref{sec:user} have been tested with several hundred users (of which about \activeUserCount were active during the course of the study), but the scalability of the visualizations must be further investigated for web services with tens of thousands of users.

@@

  \subsection*{Limitations of the Current Evolution Approach}

@@

  \subsection*{Ease of Use}

    - We designed the dashboard to make it easy to adopt. However, we still have to run a study on the challenges and opportunities of the adoption of such a dashboard.

>>>>

  \subsection*{Limitations of the Measurements}
    One limitation of the benchmarking is that it does not use a more realistic mix of workload, but rather, measures individual endpoints. It might be that multiple concurrent and diverse endpoints would have different performance impact. In fact, based on the data in the dashboard one could actually construct a statistically relevant workload mix.

  \subsection*{Lack of Proof of Adoptability}

    We designed the dashboard to make it easy to adopt and we think this is to a certain degree apparent. However, we have only presented a single use case where the API developers have used the dashboard. It would be worthwile to organize a dedicated study to observe the challenges and opportunities of the adoption of such a dashboard. It will also be important to see whether the perspectives presented here are relevant for other developers, and also which other perspectives are missing.

  % \subsection*{Limitation of Visualizations }

  %   The visualizations for the user experiene perspectives as presented in Section \ref{sec:user} have been tested with several hundred users (of which about \activeUserCount were active during the course of the study), but the scalability of the visualizations must be further investigated for web services with tens of thousands of users.

@@

  \subsection*{Limitations of the Current Approach to Evolution Monitoring}

@@
